Healthcare Insights and Sociodemographic Analysis of New York: A Comprehensive Analysis of Patient Records in 2013

### 2023-09-28 STAT405Project.qmd
Update STAT405Project.qmd

---
title: "Healthcare Insights and Sociodemographic Analysis of New York: A Comprehensive Analysis of Patient Records in 2013"
format: pdf
author: Abel Limachi, Austin Tran, Joel Villarino, and Krish Kumar (Group 3)
editor: visual
---
*(last updated 09/23/2023)*

@@

```{r}
#| echo: false
#install.packages("readr")
library(readr)

data_set <- read_csv("Hospital_Inpatient_Discharges__SPARCS_De-Identified___2013.csv",show_col_types = FALSE)

@@

```{r}
#| echo: false
length_of_stay <- strtoi(cleaned_data$`Length of Stay`)
plot(length_of_stay, y,  xlab = "Length of Stay", main = "Price vs Length of Stay", ylab = "Price")

lmfs <- lm(y ~ length_of_stay)
summary(lmfs)
abline(lmfs, col = "RED")
```

@@

```{r}
#| echo: false
#install.packages("ggplot2")
library(ggplot2)
ggplot(cleaned_data, aes(x = Gender, fill = Race)) +
  geom_bar() +
  labs(
    title = "Stacked Bar Chart by Gender and Race",
    x = "Gender",
    y = "Count"
  ) +
  scale_fill_manual(
    values = c("White" = "lightblue", "Black" = "lightcoral", "Other" = "lightgreen"),
    name = "Race"
  ) +
  scale_y_continuous(labels = scales::comma)
  theme_minimal()

@@

## **Plot 8:
```{r}
#| echo: false
#install.packages("ggplot2")
library(ggplot2)
ggplot(cleaned_data) + 
        aes("Race", "Total Costs", color = "salmon") + 
        geom_jitter()

@@

>>>>

---
title: "Healthcare Insights and Sociodemographic Analysis of New York: A Comprehensive Analysis of Patient Records in 2013"
format: pdf
author: Abel Limachi, Austin Tran, Joel Villarino, and Krish Kumar (Group 3)
editor: visual
---

*(last updated 09/23/2023)*

@@

```{r}
#| echo: false
#install.packages("readr")
#install.packages("xtable")
library(readr)
library(xtable)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
data_set <- read_csv("Hospital_Inpatient_Discharges__SPARCS_De-Identified___2013.csv",show_col_types = FALSE)

@@

```{r, results='asis'}
#| echo: false
length_of_stay <- strtoi(cleaned_data$`Length of Stay`)
plot(length_of_stay, y,  xlab = "Length of Stay", main = "Price vs Length of Stay", ylab = "Price")

lmfs <- lm(y ~ length_of_stay)
xtable(lmfs, comment = FALSE)
abline(lmfs, col = "RED")
```

@@

```{r}
#| echo: false
#install.packages("ggplot2")
library(ggplot2)
ggplot(cleaned_data, aes(x = Gender, fill = Race)) +
  geom_bar() +
  labs(
    title = "Stacked Bar Chart by Gender and Race",
    x = "Gender",
    y = "Count"
  ) +
  scale_fill_manual(
    values = c("White" = "lightblue", "Black" = "lightcoral", "Other" = "lightgreen"),
    name = "Race"
  ) +
  theme_minimal()

@@

## Plot 8: Boxplots on the Total Costs on the Risk of Mortality

```{r warning = FALSE}
#| echo: false
#install.packages("ggplot2")
ggplot(cleaned_data) + 
  aes(x = cleaned_data$'APR Risk of Mortality', y = cleaned_data$"Total Costs", color = "salmon") + 
  geom_boxplot() +
  labs(title = "Total Costs on Risk of Mortality",
       x = "APR Risk of Mortality",  # X-axis title
       y = "Total Costs")  # Y-axis title

@@

## Plot 9: Boxplots on the Total Costs on the Risk of Mortality

## Plot 10:

## Plot 11:

## Plot 12:
